---
output:
  pdf_document: default
  html_document: default
---
# Use of python as engine
In Rmarkdown, different engines can be used (). To combine Python and R scripts, the R package reticulate will do the hard work to enable interoperability of R an Python code chunks in your Rmarkdown document (https://rstudio.github.io/reticulate/articles/r_markdown.html).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# This is the library that takes care of R/Python integration
library(reticulate)
reticulate::use_python("c:/Users/stolte/AppData/Local/Continuum/anaconda3/python.exe")
reticulate::py_available()
# use_condaenv("base")
# reticulate::conda_create("matplotlib")
reticulate::conda_install(packages = "matplotlib")
# In Python you typically use a virtual environment
# use_virtualenv("main")
```


Install python packages if necessary. see also https://rstudio.github.io/reticulate/articles/python_packages.html for installation from within R.


## Python Markdown
This is an example of how to include python in a markdown document. 


```{python}
import pandas as pd
import numpy as np

x = np.arange(10)
y = x**2
df = pd.DataFrame(data=dict(x=x, y=y))
df.plot('x',  'y')
```


## Using python in R Markdown

We can  even switch back and forth to to R. Let's call the `summary` function, for which there is no python equivalent. 

```{r}
summary(py$df)
```

## Including R plots based on python data.

We can also use the `ggplot2` package,  which provides an elegant interface. It is based on the "grammar of graphics". 

```{r, echo=FALSE}
library(ggplot2)
ggplot(py$df,  aes(x, y)) + geom_point()
```

## Back to python
We can load a dataset in R using the data function. Let's take the `cars` example dataset.
```{r cars}
summary(cars)
help(cars)
```

Now we can plot the same variable  in python.
```{python}
import matplotlib.pyplot as plt
(fig, ax) = plt.subplots()
r.cars.plot('speed', 'dist', ax=ax)
ax.set_xlabel('Speed [mph]')
ax.set_ylabel('Stopping distance [ft]')
```
 